---
title: "trytaimaar"
output:
  word_document: default
  html_document: default
date: "2023-09-25"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(reshape2) 
library(dplyr)
library(ggplot2)
```
load necessary packages

```{r}
mutpersist <- read_delim("/Users/abuzarbhatty/Downloads/100pop1.csv", delim = "\t", escape_double = FALSE,  col_types = cols(cycle = col_character(),  count_p1 =   col_number(), count_p2 = col_number()),  trim_ws = TRUE) 
```
loads the desired file, HAVE TO USE EXACT FILE PATH

```{r}
mutpersist$cycle <- as.numeric(mutpersist$cycle)
preparelist <- mutpersist
preparelist2 <- preparelist[order(preparelist$cycle), decreasing = FALSE]
preparelist2 <- preparelist2%>%filter( (cycle > 4900 | row_number() == 1 ))
start4901 <- preparelist2%>%filter( (cycle < 4911 | row_number() == 1 ))
end5001 <- preparelist2%>%filter( (cycle > 4991 | row_number() == 1 ))
start4901$cycle <- as.character(start4901$cycle)
end5001$cycle <- as.character(end5001$cycle)
```
prepares the file to be parsed. Splits the entire data set into 2 seperate datasets: 4901 runs and 5001 runs

```{r}
yesno4901 <- start4901 %>% mutate_if(is.numeric, ~(1) * (. != 0))
yesno5001 <- end5001 %>% mutate_if(is.numeric, ~2 * (. != 0))

```
prepares dataset to be parsed even further. If number of individuals with mutation is higher than 0, for 4901 runs the number is replaced with the number 1, for 5001 runs the number us replaces with 2

```{r}
pop1 <- yesno4901$count_p1 + yesno5001$count_p1
pop2 <- yesno4901$count_p2 + yesno5001$count_p2
keptorlost <- cbind(pop1,pop2)
keptorlost <- as.data.frame(keptorlost)
```
lets us about status of mutation. 

3 = mutation present at 4901 and persisted till 5001
2 = mutation not originally present at 4901, but present at end of generation 5001
1 = mutation present at 4901, lost at the end of generation 5001
0 = mutation not present at 4901, not present at 5001 either

```{r}
# Open a jpg file
jpeg("chanceofmutationppresistingp1.jpg", width = 500, height = 500)
# 2. Create a plot
ggplot(keptorlost, aes(x = pop1)) + geom_bar()
# Close the pdf file
dev.off()

# Open a jpg file
jpeg("chanceofmutationppresistingp2.jpg", width = 500, height = 500)
# 2. Create a plot
ggplot(keptorlost, aes(x = pop2)) + geom_bar()
# Close the pdf file
dev.off()
```
